Capstone Movielens Report

### 2025-05-02 reports/capstone-movielens-report.draft4.Rmd
Version 4 of the RMD report added.

```{r setup, include=TRUE, echo = FALSE}
if(!require(tidyverse))
  install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require(caret))
  install.packages("caret", repos = "http://cran.us.r-project.org")
if(!require(data.table))
  install.packages("data.table", repos = "http://cran.us.r-project.org")

@@

@@

library(caret)
library(cowplot)
library(data.table)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(lubridate)
library(Metrics)
library(recosystem)
library(scales)
library(stringr)
library(tibble)
library(tidyr)

@@

p_load(latex2exp)

>>>>

```{r setup, include=TRUE, echo = FALSE}
## Setup -----------------------------------------------------------------------
#> Reference: Some ideas and code snippers were used from the following GitHub repository:
#> https://github.com/AzKurban-edX-DS/harvardx-movielens

if(!require(tidyverse))
  install.packages("tidyverse", repos = "http://cran.us.r-project.org")

#> `stringr` library is already included to the `tidyverse` package,
#> there's no need to install `stringr`
# if(!require(stringr))
#   install.packages("stringr")

if(!require(caret))
  install.packages("caret", repos = "http://cran.us.r-project.org")
if(!require(data.table))
  install.packages("data.table", repos = "http://cran.us.r-project.org")
if(!require(gridExtra))
  install.packages("gridExtra")
if(!require("logr")) 
  install.packages("logr")

@@

if(!require("recommenderlab")) 
  install.packages("recommenderlab")

@@

library(caret)
library(cowplot)
library(data.table)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(lubridate)
library(Metrics)
library(recosystem)
library(recommenderlab)

library(scales)
library(stringr)
library(tibble)
library(tidyr)
library(gridExtra)
library(logr)

@@

p_load(conflicted, latex2exp, kableExtra)

#p_load(latex2exp)

### Resolve conflicts ----------------------------------------------------------

# For functions with identical names in different packages, ensure the
# right one is chosen:
conflict_prefer("first", "dplyr", quiet = TRUE)
conflict_prefer("count", "dplyr", quiet = TRUE)
conflict_prefer("select", "dplyr", quiet = TRUE)
conflict_prefer("group_by", "dplyr", quiet = TRUE)
conflict_prefer("ungroup", "dplyr", quiet = TRUE)
conflict_prefer("summarise", "dplyr", quiet = TRUE)
conflict_prefer("summarize", "dplyr", quiet = TRUE)
conflict_prefer("distinct", "dplyr", quiet = TRUE)
conflict_prefer("top_n", "dplyr", quiet = TRUE)
conflict_prefer("arrange", "dplyr", quiet = TRUE)
conflict_prefer("mutate", "dplyr", quiet = TRUE)
conflict_prefer("semi_join", "dplyr", quiet = TRUE)
conflict_prefer("left_join", "dplyr", quiet = TRUE)
conflict_prefer("filter", "dplyr", quiet = TRUE)
conflict_prefer("slice", "dplyr", quiet = TRUE)
conflict_prefer("glimpse", "dplyr", quiet = TRUE)
conflict_prefer("union", "dplyr", quiet = TRUE)

conflict_prefer("pivot_wider", "tidyr", quiet = TRUE)
conflict_prefer("kable", "kableExtra", quiet = TRUE)
conflict_prefer("year", "lubridate", quiet = TRUE)
conflicts_prefer(base::as.matrix)
